### 2015-01-17 src/introduction.Rnw
added for alex

% For a mutation selection strategy to be considered effective, especially during
% the development, it should be able to expose as many defect-like behaviors as
% possible.
Consider any test in a test suite. It is written with the intent of
checking for the absence of some (faulty) behavior. From the perspective of a
a tester, the best testsuite is one that checks for the absence
of the largest number of faulty behaviors. If tests were equivalent in the
amount of behaviors that they verify, then the best testsuite would be one that
encouraged adding the largest number of non-redundant test cases. However,
it is possible that different tests are not equivalent in the number of
behaviors that they check. We can approximate this to some extent by
including the number of assert statements within each test~\footnote{We
approximate the effect of exception-only test cases by starting the assert
count from $1$ rather than $0$}.

>>>>

% For a mutation selection strategy to be considered effective, especially during
% the development, it should be able to expose as many defect-like behaviors as
% possible.

% Alex: added
Given a set of mutants and a universe of test cases, we can approximate the
minimal set of test cases required to kill those mutants.\footnote{We only
approximate this, with greedy methods, due to the high cost of computing a
perfect minimal set, as established in the test case selection literature
\cite{YooHarman}.}  Ideally, we would like a set of mutants that require
as many test cases as possible, if we assume that the original set of test
cases is populated with useful, non-redundant test cases.  While the suites
of many open source programs are far from adequate, they should satisfy that
requirement:  each test was almost always added by considerable manual labor,
and was at least believed to be useful.  Therefore, any tests omitted likely
indicate a potential to miss faults.  A good mutation selection strategy,
therefore, should 1) be as close to the original set of mutants as possible,
in terms of the test cases it requires in a minimal suite and 2) require
more test cases than a randomly selected set of mutants of the same size.

All test cases are not created equal, of course -- we use assertion counts
and execution time as other measures.

% Alex: rm
% Consider any test in a test suite. It is written with the intent of
% checking for the absence of some (faulty) behavior. From the perspective of a
% a tester, the best testsuite is one that checks for the absence
% of the largest number of faulty behaviors. If tests were equivalent in the
% amount of behaviors that they verify, then the best testsuite would be one that
% encouraged adding the largest number of non-redundant test cases. However,
% it is possible that different tests are not equivalent in the number of
% behaviors that they check. We can approximate this to some extent by
% including the number of assert statements within each test~\footnote{We
% approximate the effect of exception-only test cases by starting the assert
% count from $1$ rather than $0$}.
